---
title: "Control chart"
output: html_document
---
#**dfphase1 library**
```{r}
# A simulated example
#install.packages("dfphase1")
library(dfphase1)
set.seed(12345)
y <- matrix(rt(100,3),5)
y[,20] <- y[,20]+3
y
```

```{r}
shewhart(y)
```
```{r}
# Reproduction of the control charts shown
# by Jones-Farmer et. al. (2009,2010)
data(colonscopy)
colonscopy
```

```{r}

u <- shewhart.normal.limits(NROW(colonscopy),NCOL(colonscopy),stat="lRank",FAP=0.1)
# control limits based on a limited number of replications
# to avoid a (relatively) long execution time
shewhart(colonscopy,stat="lRank",limits=u,L=10000)
shewhart(colonscopy,stat="sRank",FAP=0.1,L=10000)
```


#**ggQC Control Charts**
```{r}
library(tidyverse)
library(ggQC)
```


```{r}
set.seed(5555)
Process_Data <- 
  data.frame(
   Process=rep(c("A"), each = 30), #Process A 
   Run_Number=c(1:30),             #Run Order    
   Value = c(rnorm(n = 30, mean = 30.5, sd = 1)) #Process A Random Data
   )
Process_Data
```


```{r}
### Make the plot
XmR_Plot <- 
  ggplot(Process_Data, aes(x = Run_Number, y = Value)) + #init ggplot
  geom_point() + geom_line() + # add the points and lines
  stat_QC(method = "XmR",      # specify QC charting method
          auto.label = T,      # Use Autolabels
          label.digits = 2,    # Use two digit in the label
          show.1n2.sigma = T   # Show 1 and two sigma lines
          ) +  
  scale_x_continuous(expand =  expand_scale(mult = .15))  # Pad the x-axis
 
### Draw the plot - Done
XmR_Plot
```

By building upon the ggplot framework, you get a high level of control over the plot details such as points and lines etc. In addition, if you want to put XmR and mR data on the same plot, you can. Just make multiple calls to the stat_QC() command, as shown below.
```{r}
### Two stat_QC calls
XmR_Plot <- 
  ggplot(Process_Data, aes(x = Run_Number, y = Value)) + #init ggplot
  geom_point() + geom_line() + #add the points and lines
  stat_QC(method = "XmR", #specify QC charting method
          auto.label = T, # Use Autolabels
          label.digits = 2, #Use two digit in the label
          show.1n2.sigma = T  #Show 1 and two sigma lines
          ) +  
  stat_QC(method="mR") +
  scale_x_continuous(expand =  expand_scale(mult = .15))  # Pad the x-axis
 
### Draw the plot - Done
XmR_Plot
```

# Violation Analysis

Same Side: 8 or more consecutive, same-side points
1 Sigma: 4 or more consecutive, same-side points exceeding 1 sigma
2 Sigma: 2 or more consecutive, same-side points exceeding 2 sigma
3 Sigma: any points exceeding 3 sigma
```{r}
#Uses the same data as previous example. 
 
QC_Violations <- 
  ggplot(Process_Data, aes(x = Run_Number, y = Value)) + #init ggplot
  stat_qc_violations(method = "XmR" 
                     #show.facets = 4 #if you just want facet 4
                     )
QC_Violations
```
# Capability Analysis

```{r}
# Uses the same data as the first example
CapabilityAnaylsis <- 
 ggplot(Process_Data, aes(x = Value)) + #init ggplot
  geom_histogram(binwidth = .75, color="purple") + #make the histogram
  stat_QC_Capability(
    LSL=25, USL=37,                    #Specify LSL and USL
    show.cap.summary = c("Cp", "Cpk"), #selected summary
    digits = 2,                        #report two digits
    method="XmR") +                    #Use the XmR method
scale_x_continuous(expand =  expand_scale(mult = c(0.15,.65))) #pad the X-axis 
 
#plot the graph
CapabilityAnaylsis
```
# Pareto Analysis
```{r}
#load your data
Data4Pareto <- data.frame(
  KPI = c("Customer Service Time", "Order Fulfillment", "Order Processing Time",
        "Order Production Time", "Order Quality Control Time", "Rework Time",
        "Shipping"),
  Time = c(1.50, 38.50, 3.75, 23.08, 1.92, 3.58, 73.17)
) 
 
#make the plot
ggplot(Data4Pareto, aes(x=KPI, y=Time)) +
 stat_pareto(point.color = "red",
             point.size = 3,
             line.color = "black",
             bars.fill = c("blue", "orange")
             ) +
  theme(axis.text.x = element_text(angle = 90, hjust = 1, vjust=0.5))
 
#done
```

# **qcc library**
```{r}
chartdata <- read.table(header = FALSE, text = "
  0.731
  0.734
  0.733
  0.734
  0.733
  0.734
  0.734
  0.733
  0.734
  0.715
  0.734
  0.732
  0.735
  0.734
  0.734
  0.731
  0.731
  0.735
  0.713
  0.731
  0.715
  0.736
  0.733
  0.733
  0.732
  0.732
  0.733
  0.715
  0.734
  0.734
  ")
```


```{r}
#install.packages("qcc")
library(qcc)
```

```{r}
chartdata
```

```{r}
qcc(data = chartdata, # The dataset
    type = "xbar.one", # The chart type (in this case it lets qcc know that n = 1)
    plot = TRUE) # Display the plot
```
Create a x-bar chart for n >1 and customize the chart

Now we will plot an x-bar chart where n > 1. First we will read in the data. We will again do this using read.table but this time we will have 25 samples of n = 5 where each observation is contained in a different column.
```{r}
chartdata2 <- read.table(header = FALSE, text = "
  0.07705     0.076030001 0.076959997 0.075489998 0.076920003
  0.078160003 0.077119999 0.076250002 0.076690003 0.076470003
  0.077550001 0.077079996 0.077129997 0.076839998 0.077440001
  0.07581     0.07728     0.076549999 0.077760004 0.077540003
  0.077459998 0.079109997 0.077830002 0.07711     0.078670003
  0.0766      0.078039996 0.076240003 0.077660002 0.075900003
  0.077919997 0.074440002 0.078419998 0.077370003 0.074500002
  0.077299997 0.076370001 0.075539999 0.076800004 0.078280002
  0.075460002 0.076229997 0.077959999 0.07491     0.078620002
  0.07931     0.077420004 0.07519     0.07784     0.07649
  0.076609999 0.076860003 0.077720001 0.075790003 0.078380004
  0.078050002 0.075450003 0.078400001 0.076810002 0.077770002
  0.077289999 0.078170002 0.077260002 0.076849997 0.075120002
  0.077639997 0.076820001 0.077200003 0.079180002 0.078299999
  0.077610001 0.075630002 0.079350002 0.076920003 0.075800002
  0.076509997 0.076970004 0.077919997 0.078189999 0.077660002
  0.07863     0.077200003 0.077310003 0.076530002 0.075680003
  0.075730003 0.07807     0.075580001 0.074589998 0.076499999
  0.076849997 0.076140001 0.077370003 0.075790003 0.07705
  0.076370001 0.076700002 0.075620003 0.077399999 0.076559998
  0.076180004 0.078189999 0.07626     0.076580003 0.077459998
  0.076059997 0.075350001 0.077310003 0.07553     0.077990003
  0.076889999 0.075240001 0.076609999 0.077090003 0.079120003
  0.07762     0.078919999 0.078730002 0.076849997 0.077660002
  0.078299999 0.075479999 0.076619998 0.078780003 0.07728")
chartdata2
```

```{r}
xbar_chart2 <- qcc(data = chartdata2,
                   type = "xbar",
                   sizes = 5,
                   title = "Sample X-bar Chart Title", # Replacement title
                   digits = 2, # Limit the signifciant figures
                   plot = TRUE)
```


```{r}
xbar_chart2
```
We can improve the plot visually by customizing the colors using the following code to set the background to grey and the margins to white.

```{r}
qcc.options(bg.margin = "white", bg.figure = "gray95")

```


```{r}
xbar_chart2 <- qcc(data = chartdata2,
                   type = "R",
                   sizes = 5,
                   title = "Sample R Chart Title",
                   digits = 2,
                   plot = TRUE)
```

Create an R chart

Finally, to create an r chart we repeat the process above except now we will specify that we want an r chart instead of an x-bar chart. Note that the color scheme remains altered since we changed qcc.options above.
```{r}
xbar_chart2 <- qcc(data = chartdata2,
                   type = "R",
                   sizes = 5,
                   title = "Sample R Chart Title",
                   digits = 2,
                   plot = TRUE)
```
```{r}
# loading package
library(qcc)
# Loading the piston rings data
data(pistonrings)
attach(pistonrings)
head(pistonrings)
```


```{r}
diameter <- qcc.groups(diameter, sample)
head(diameter)
summary(diameter)
```


```{r}
obj <- qcc(diameter[1:30,], type="R")
```


```{r}
summary(obj)
```


```{r}
obj <- qcc(diameter[1:30,], type="xbar")
```


```{r}
summary(obj)
```
Let’s see what happen if I change the nsigma to 2.
```{r}
obj <- qcc(diameter[1:30,], type="xbar",nsigmas = 2)
```
As it can be seen from the plot, 3 observation points goes out of control. This is because we make control limits tighter.
Let’s see for nsigma=1.

```{r}
obj <- qcc(diameter[1:30,], type="xbar",nsigmas = 1)
```

Step 4

The last step is to test for new data. Now, so far, we know that for nsigma=3, the process is in control. We can use the computed control limits for monitoring new sample data from the same process.
```{r}
obj <- qcc(diameter[1:30,], type="xbar",newdata=diameter[31:40,])
```


```{r}
data(orangejuice)
orangejuice
```


```{r}
library(tidyverse)
library(qcc)
library(scales)

data("orangejuice")
orangejuice
u_chart_obj <- with(orangejuice, qcc(D, sizes = size, type = 'u'))

oj <- mutate(orangejuice, 
             row_id = 1:nrow(orangejuice),
             # identify rows of interest
             beyond_limits = row_id %in% u_chart_obj$violations$beyond.limits,
             violating_runs = row_id %in% u_chart_obj$violations$violating.runs,
             # data for plotting control limits
             center = u_chart_obj$center,
             lcl = u_chart_obj$limits[1, 'LCL'],
             ucl = u_chart_obj$limits[1, 'UCL'])

oj
```
```{r}
update_geom_defaults('point', list(size = 3))

ggplot(oj, aes(sample, D/size)) + 
  # create a basic chart with dots and lines
  geom_line(color = 'gray', size = 0.5) +
  geom_point() + 
  # mark certain points red or gold
  geom_point(color = 'red', data = filter(oj, beyond_limits)) +
  geom_point(color = 'gold', data = filter(oj, violating_runs)) +
  # add the control limits and center line
  geom_hline(aes(yintercept = lcl), linetype = 'dashed') +
  geom_hline(aes(yintercept = ucl), linetype = 'dashed') +
  geom_hline(aes(yintercept = center)) +
  # express y axis labels in 'per million'
  scale_y_continuous(labels = unit_format(scale = 1e6, unit = '')) +
  # misc cleanup
  theme_light() +
  labs(x = 'Sample Number', y = 'Defects per million units')
```


```{r}
data2 <- data %>%
  arrange(Date) %>%
  mutate(date.diff = c(NA, diff(Date))) %>%
  mutate(is.gap = !is.na(date.diff) & date.diff > median(date.diff, na.rm = TRUE)) %>%
  mutate(period.id = cumsum(is.gap))
head(data2)
```


```{r}
data2 <- data2 %>%
  select(-date.diff, -is.gap) %>% # drop unneeded columns
  tidyr::gather(color, y, -Date, -period.id) %>%
  mutate(color = factor(color,
                        levels = c("Return", "PredReturn")))
head(data2)
```

```{r}
p <- ggplot(data2,
       aes(x = Date, y = y, color = color)) +
  geom_line() +
  facet_grid(~ period.id, scales = "free_x", space = "free_x") +
  scale_color_manual(values = c("Return" = "black",
                                "PredReturn" = "red")) +
  theme_light()

p
```


```{r}
p +
  scale_x_datetime(expand = c(0, 0),             # remove space within each panel
                   breaks = "5 days") +          # specify desired time breaks
  theme(panel.spacing = unit(0, "pt"),           # remove space between panels
        axis.text.x = element_text(angle = 90))  # rotate x-axis text
```

# x-bar chart
```{r}
library(qcc)
data(pistonrings)
pistonrings
```


```{r}
diameter <- qccGroups(diameter, sample, data = pistonrings)

diameter <- qcc.groups(diameter, sample,data = pistonrings)
head(diameter)
```


```{r}
data(pistonrings)
attach(pistonrings)
# create a matrix of 40 samples made of 5 observations each
diameter <- qcc.groups(diameter, sample)
head(diameter)
```


```{r}
q1 <- qcc(diameter[1:25,], type="xbar", newdata=diameter[26:40,])
q1
```

```{r}
q1 <- qcc(diameter, type="xbar")
```

```{r}
q1 <- qcc(diameter, type="R")

```

```{r}
```

