---
title: "R Notebook"
output: html_document
---

#BEGIN HERE----------------
```{r}
#install.packages("data.table")
```


```{r}
library(data.table)
library(tidyverse)
library(lubridate)
setDTthreads(threads = 0)
getDTthreads(verbose=TRUE) 

packageVersion("data.table") # ‘1.13.2’ --> v1.13.6
```

```{r}
#file='/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_3000_head.dat' 
#file='/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_4000.dat' # 0.8 GB
#file='/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_4000_tail.dat'
#file='/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_3000.dat'# 3.6 GB
#file<-'/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_E_series.dat' # 2.9 GB crack session (ram?)
#file<-'/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_Ric.dat' # 2.8 GB OK

#file <- "//Vn01w2k16v18/data/Copyroom/Test_software/Data/V04R-V04R-SQLData_Ric.dat" # 2.24 GB
#file <- "//Vn01w2k16v18/data/Copyroom/Test_software/Data/V04R-V04R-SQLData_3000.dat" # 3.6 GB
#file <- "//Vn01w2k16v18/data/Copyroom/Test_software/Data/V04R-V04R-SQLData_4000.dat" # 0.8 GB
file <- "//Vn01w2k16v18/data/Copyroom/Test_software/Data/V04R-V04R-SQLData_4000_tail.dat" # 251 MB
#file <- "//Vn01w2k16v18/data/Copyroom/Test_software/Data/V04R-V04R-SQLData_Eseries.dat" # 2.9 GB Crash seasion at 7.4 GB
data_head<-fread(file,fill=TRUE,nrows=5)
data_head # month/day/year
```
# Cut data
```{r}
#min line 4000 : 9/5/2019, max line 4000: 4/11/2020
# dim line 4000 :1404350 
#data_cut_off<-fread(file,fill=TRUE,skip=804350)
#dim(data_cut_off)
#data_cut_off
```

```{r}
#fwrite(data_cut_off,file='/media/ad/01D6B57CFBE4DB20/1.Linux/Data/FQC/V04R-V04R-SQLData_4000_tail.dat')
```

# Begin analysis
```{r}
#install.packages('doParallel')
#Method 1
#library(doParallel)
#no_cores <- detectCores()
#print(no_cores)
#cl <- makeCluster(no_cores)  
#registerDoParallel(cl)  

```
```{r}
#Method 2
#library(doParallel)
#cl <- makePSOCKcluster(5)  
#registerDoParallel(cl)  
```


```{r}
start.time <- Sys.time()

product_type_column='V3'
tryCatch(
  expr    = {dt1 <<- fread(file,fill=TRUE,select=c(product_type_column))},
  warning = function(w){
    cat('Warning: ', w$message, '\n\n');
    n_line <- as.numeric(gsub('Stopped early on line (\\d+)\\..*','\\1',w$message))
    if (!is.na(n_line)) {
      cat('Found ', n_line,'\n')
      dt1_part1 <- fread(file,fill=TRUE, nrows=n_line-1,select=c(product_type_column))
      dt1_part2 <- fread(file,fill=TRUE,skip=n_line,select=c(product_type_column))
      dt1 <<- rbind(dt1_part1, dt1_part2, fill=T)
    }
  },
  finally = cat("\nFinished. \n")
  #finally=.Call(CfreadCleanup)
);
end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken 
# No Parallel: 1.118 mins
# doParallel method 1: 1.097 mins --> run lan 2 la 58 or 52 s 
# doParallel method 2: 1.118 mins
# doParallel method 3: 51 s
```
Read 2.4 GB Ric data, Ram from 5.3 GB --> 7 GB --> 5.2 GB (25 s). object size 29 MB
Read 3.6 GB Rec 3000 data, Ram from 5.2 GB --> 7.2 GB --> 5.3 GB -->7.2-->4.7 (1.8 min). object size 43 MB
```{r}
#install.packages("pryr")
library(pryr)
object_size(dt1) # 43.7 MB
```


```{r}
#product_type_column='V3'
#dt1<-fread(file,fill=TRUE,select=c(product_type_column))
dim(dt1)
head(dt1)
tail(dt1)
```
```{r}
class(dt1)
```


```{r}
product_all <- as.data.frame(table(dt1)) %>% 
  arrange(desc(Freq)) %>% 
  top_n(20,Freq)
product_all
```
```{r}
product_all %>% 
  ggplot(aes(x= reorder(dt1, -Freq),y=Freq)) +
  geom_bar(stat="identity",fill="steelblue")+
  theme(axis.text.x=element_text(angle=90))
```
#**Choose all parameter**
```{r}
# Please choose product_type:
product_type='3105471-p41AA015_8Q'
#product_type='31A007G_P'
# Please choose parameter column to show
parameter_column_name='V65'
parameter_column_value='V66'
# Default time column:
product_type_column='V3'
date_column='V6'
```

```{r}
start.time <- Sys.time()
tryCatch(
  expr    = {dt2 <<- fread(file,fill=TRUE,select=c(product_type_column,date_column,parameter_column_name,parameter_column_value)) %>% 
    filter(V3 ==product_type)
  },
  warning = function(w){
    cat('Warning: ', w$message, '\n\n');
    n_line2 <- as.numeric(gsub('Stopped early on line (\\d+)\\..*','\\1',w$message))
    if (!is.na(n_line2)) {
      cat('Found ', n_line2,'\n')
      dt2_part1 <- fread(file,fill=TRUE, nrows=n_line2-1,select=c(product_type_column,date_column,parameter_column_name,parameter_column_value))
      dt2_part2 <- fread(file,fill=TRUE,skip=n_line2,select=c(product_type_column,date_column,
                                                          parameter_column_name,parameter_column_value))
      dt2 <<- rbind(dt2_part1, dt2_part2, fill=T)%>% 
      filter(V3 ==product_type)
    }
  },
  finally = cat("\nFinished. \n")
);
end.time <- Sys.time()
time.taken <- end.time - start.time
time.taken # 1.1207 mins , run lan 2: 46.15 s
# Method 3: 43 s
```


```{r}
dim(dt2) # 196766
head(dt2)
tail(dt2)
```

```{r}
colnames(dt2) <- c("product_type", "date","parameter_freq","parameter_value")
dt2
```


```{r}
print(dim(dt2))
sl<-object.size(dt2)
print(sl, units = "auto", standard = "SI") 
```
```{r}
data_all_day <- dt2 %>%
  mutate( date_trans=mdy_hms(date), # must have mdy_hms for convert date time
          date_filter=as_date(date_trans),
         )
head(data_all_day)
tail(data_all_day)
```

```{r}
#rm(dt2)
```

```{r}
min(data_process$date)
max(data_process$date)
```

#**Select one date**
```{r}
# Best to choose
date_choose="2020-06-10"
data_one_day <- data_all_day %>% 
  select(date_trans,date,date_filter,parameter_freq,parameter_value) %>% 
  filter(date_filter==ymd(date_choose))
data_one_day
```
#**Descreptive statistics**
```{r}
summary(data_one_day)
```
```{r}
#install.packages('pastecs')
library(pastecs)
stat.desc(data_one_day %>% select(parameter_freq,parameter_value))
```
```{r}
#install.packages('Hmisc')
library(Hmisc)
describe(data_one_day %>% select(parameter_freq,parameter_value))
```

```{r}
#install.packages('psych')
library(psych)
describe(data_one_day %>% select(parameter_freq,parameter_value))
```
#**Remove outlier**
```{r}
select_data<-data_one_day$parameter_value
Q1 <- quantile(select_data, .25)
Q3 <- quantile(select_data, .75)
IQR <- IQR(select_data)
k=3
data_one_day_no_outlier <- subset(data_one_day, select_data> (Q1 - k*IQR) & select_data< (Q3 + k*IQR))

print(dim(data_one_day))
print(dim(data_one_day_no_outlier))
```
```{r}
select_data<-data_all_day$parameter_value
Q1 <- quantile(select_data, .25)
Q3 <- quantile(select_data, .75)
IQR <- IQR(select_data)
k=3
data_all_day_no_outlier <- subset(data_all_day, select_data> (Q1 - k*IQR) & select_data< (Q3 + k*IQR))

print(dim(data_all_day))
print(dim(data_all_day_no_outlier))
```

#** Line PLOT**
## Dygraphs
```{r}
#install.packages('highcharter')
library(dygraphs)
```

```{r}
#df_plot
```
```{r}
# Plot value only with outlier:
plot_dygraph <- dygraph(data_one_day %>% select(date_trans,parameter_value)) %>%
  dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE )%>% 
  dyRangeSelector()
plot_dygraph
```

```{r}
str(df_plot_no_outlier)
```
```{r}
head(df_plot_no_outlier)
```

```{r}
# Plot value only with out outlier:
plot_dygraph <- dygraph(data_one_day_no_outlier %>% select(date_trans,parameter_value)) %>%
  dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE)%>% 
  dyRangeSelector()
plot_dygraph
```
```{r}
class(df_plot_no_outlier)
```
```{r}
# create the time series
temperature <- ts(frequency = 12, start = c(1980, 1),
              data = c(7.0, 6.9, 9.5, 14.5, 18.2, 21.5, 
                       25.2, 26.5, 23.3, 18.3, 13.9, 9.6))

class(temperature)
temperature
```

```{r}
# Plot value and frequency :
dy_graph <- list(
  dygraph(data_one_day_no_outlier %>% select(date_trans,parameter_value), main = "db", group = "chart")%>%
  dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE ),
dygraph(data_one_day_no_outlier %>% select(date_trans,parameter_freq), main = "Frequency", group = "chart")%>%
  dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE )
)  # end list

# render the dygraphs objects using htmltools
htmltools::browsable(htmltools::tagList(dy_graph))
```
## High charter
```{r}
#install.packages("highcharter")
library(highcharter)
```
```{r}
data_one_day_no_outlier%>%
  hchart(type = "line", hcaes(x = as.character(date_trans), y = parameter_value))
```
```{r}
data_all_day_no_outlier%>%
  hchart(type = "line", hcaes(x = as.character(date_trans), y = parameter_value))
```

```{r}
data_all_day_no_outlier%>%
  hchart(type = "line", hcaes(x = date_trans, y = parameter_value))
```

```{r}
data_all_day_no_outlier%>%
  hchart(type = "line", hcaes(x = as.character(date_trans), y = parameter_freq))
```
# Box plot
```{r}
data_all_day_no_outlier
```

#**Control chart investigate**

```{r}
data_research<-df_plot_no_outlier %>% select(date_trans,parameter_value)
data_research
```

# Continuous one-at-time data
```{r}
#install.packages("ggQC")
library(qcc)
library(scales)
```

```{r}
qcc(data_research$parameter_value, type="xbar.one", std.dev = "SD")
```


```{r}
q2 = qcc(data_research$parameter_value, type="xbar.one", std.dev = "SD",
         labels=format(data_research$date_trans,"%b-%d-%H"),axes.las = 2,xlab="")
summary(q2)

```
# Try to modify qcc for better flexible
```{r}
oj <- mutate(data_research, 
             row_id = 1:nrow(data_research),
             # identify rows of interest
             beyond_limits = row_id %in% q2$violations$beyond.limits,
             violating_runs = row_id %in% q2$violations$violating.runs,
             # data for plotting control limits
             center = q2$center,
             lcl = q2$limits[1, 'LCL'],
             ucl = q2$limits[1, 'UCL'])

oj
```


```{r}
update_geom_defaults('point', list(size = 3))

ggplot(oj, aes(date_trans, parameter_value)) + 
  # create a basic chart with dots and lines
  geom_line(color = 'gray', size = 0.5) +
  geom_point() + 
  # mark certain points red or gold
  geom_point(color = 'red', data = filter(oj, beyond_limits)) +
  geom_point(color = 'gold', data = filter(oj, violating_runs)) +
  # add the control limits and center line
  geom_hline(aes(yintercept = lcl), linetype = 'dashed') +
  geom_hline(aes(yintercept = ucl), linetype = 'dashed') +
  geom_hline(aes(yintercept = center)) +
  # express y axis labels in 'per million'
  scale_y_continuous(labels = unit_format(scale = 1e6, unit = '')) +
  # misc cleanup
  theme_light() +
  labs(x = 'Sample Number', y = 'Defects per million units')
```

# Hide blank space dygraph with no x-values 
```{r}
data_research<-df_plot_no_outlier %>% select(date_trans,parameter_value)
data_research
```
We can identify time gaps by comparing the time difference between consecutive time stamps. Here, the logic I used defines a gap as any time difference larger than the median of all time differences. You may want to change that to some other value (e.g. 2 days? 1 week?) depending on your context:
```{r}
date_diff <- 360 # 6 hour
data2 <- data_research %>%
  arrange(date_trans) %>%
  mutate(date.diff = c(NA, diff(date_trans))) %>%
  #mutate(is.gap = !is.na(date.diff) & date.diff > median(date.diff, na.rm = TRUE)) %>%
  mutate(is.gap = !is.na(date.diff) & date.diff > date_diff) %>%
  mutate(period.id = cumsum(is.gap))
head(data2)
```
```{r}
count(data2,is.gap)
```

```{r}
describe(data2)
```

Now each period.id value corresponds to a subset of data without major time differences within its rows. We can further wrangle this data by converting it to long format:
```{r}
data2 <- data2 %>%
  select(-date.diff, -is.gap) %>% # drop unneeded columns
  tidyr::gather(color, y, -date_trans, -period.id)

head(data2)
```
Pass this data to ggplot(), facet by time periods with free scales, & you'd have eliminated the blank spaces from the earlier plot above:

```{r}
p <- ggplot(data2,
       aes(x = date_trans, y = y)) +
      geom_line() +
      facet_grid(~ period.id, scales = "free_x", space = "free_x") +
      theme_light()+
      scale_x_datetime(expand = c(0, 0),             # remove space within each panel
                       breaks = "5 days") +          # specify desired time breaks
      theme(panel.spacing = unit(0, "pt"),           # remove space between panels
            axis.text.x = element_text(angle = 90))  # rotate x-axis text

p 
```
```{r}
library(xts) # convert date time to dygraph right format
```

```{r}
data2
str(data2)
```

```{r}
data3<-setDT(data2) # convert to data table from data frame
str(data3)
count(data3,period.id)
```
```{r}
unique(data3$period.id)

for (i in unique(data3$period.id)) {
  print(i)
}
```

```{r}
# Add points
plot_dygraph <- dygraph(data3 %>% select(date_trans,y)) %>%
  dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE)%>% 
  dyRangeSelector()
plot_dygraph
```
```{r}

for (i in unique(data3$period.id)) {
  dygraph(filter(data3, period.id==i) %>% select(date_trans,y), main = "db", group = "chart")%>%
  dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE )
}
```


```{r}
# create a list of dygraphs objects
library(dygraphs)
library(htmltools)
# Plot value and frequency :
a<-filter(data3, period.id==0)
b<-filter(data3, period.id==1)
c<-filter(data3, period.id==2)
d<-filter(data3, period.id==3)


dygraph(a %>% select(date_trans,y), main = "db", group = "chart")%>%
dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE )

dygraph(b %>% select(date_trans,y), main = "db", group = "chart")%>%
dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE )

dygraph(c %>% select(date_trans,y), main = "db", group = "chart")%>%
dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE )

dygraph(d %>% select(date_trans,y), main = "db", group = "chart")%>%
dyOptions( drawPoints = TRUE, pointSize = 4,useDataTimezone = TRUE )

#htmltools::browsable(htmltools::tagList(dy_graph))
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```


```{r}
```

